---
title: "Exploration of Arthritis-like Diseases"
---

```{r include=FALSE}
knitr::opts_chunk$set(echo=FALSE, comment = NA, message=FALSE, warning=FALSE) #<--this will remove comments, messages, & warnings
```

```{r libSets, echo=FALSE, message=FALSE}
library("googlesheets4")
library("tidyverse")
library("tidygraph")
library("ggraph")
library("googlesheets4")
library("gridExtra")
library("table1")
library("readxl")    #<- this will readin excel files
library("gridExtra") #<- this will output data in a grid format
library("wordcloud")
library("ggplot2")
library("knitr")
#### this paragraph is the knit_hook created by yihui to reduce results lines
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  lines <- options$output.lines
  if (is.null(lines)) {
    return(hook_output(x, options))  # pass to default hook
  }
  x <- unlist(strsplit(x, "\n"))
  more <- "..."
  if (length(lines)==1) {        # first n lines
    if (length(x) > lines) {
      # truncate the output, but add ....
      x <- c(head(x, lines), more)
    }
  } else {
    x <- c(more, x[lines], more)
  }
  # paste these lines together
  x <- paste(c(x, ""), collapse = "\n")
  hook_output(x, options)
})
#### ^-- end of knit_hook

gs4_deauth()

filePath <- "C:/Users/Sean/Documents/DigitCoral/DigitHerb/Cleaned/"
readIn.func <- function(fileName){
  read_excel(paste0(filePath,fileName,".xlsx"))
}
```

---

## **The concept of 风湿 (FengShi) in Chinese Herbal Medicine:**

- **FengShi, is an ancient Chinese diagnosis which included Arthritis (& Rheumatoid Arthritis,RA), Osteoporosis,  Body/Joint Pain & deformities.**
- **The etiology of this group of symptoms are considered as the invasion of 'cold' & 'moisture' essences into human body, and show significant symptoms (sore, pain, & deformation) on body muscles/bones, major joints (like knee, wrist).**

---

### **Explore Herbs' Cures Targeting 'FengShi':**
*(search keywords contain '风湿' or '风'&'湿' among herbs' 'Cures')*

```{r hb_fj_nam}

# ----------- Herb & Prescription Names ------------ 

hb_nam <- readIn.func(fileName = "Copy of HerbNames_v210807")
fj_nam <- readIn.func(fileName = "FangJiNames_v210822")

```

```{r fs_hb_cur}

# ----------- Herbs Cure FengShi ------------ 

fs_hb_cur <- readIn.func(fileName = "fs_hb_curs")

```

- **Among all <span style="color:red;fond=bold"> `r length(unique(hb_nam$Corrected_ChName))` </span> herbs collected, there are <span style="color:red;fond=bold"> `r length(unique(fs_hb_cur$Corrected_ChName))` </span> herbs' 'Cure' contain the keyword '风湿' or '风'&'湿';**

- **Among these herbs would cure FengShi, a word cloud of all their 'Cures'(or say symptoms, occurred >1 times) is shown below:**
<center>
```{r fs_hb_symp_wdcld}
fs_hb_symp_only <- select(fs_hb_cur,Symptom)
symps <- data.frame(Symptom=na.omit(unlist(fs_hb_symp_only)))
symps$Symptom <- factor(symps$Symptom,levels=as.character(names(sort(table(symps$Symptom),decreasing=T))))
symp_freq <- as.data.frame(table(symps$Symptom))
wordcloud(words=symp_freq$Var1,freq=symp_freq$Freq,min.freq=2,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8,'Dark2'))
```
</center>
- **From above word cloud, we can see that beyond '风湿', these herbs also cure '跌打损伤'(Damages by Falling & Beaten), '骨折'(Fracture), etc, which highly related to pain, tissue (muscle or bone) damages.**

---

### **Explore Herbs' Functions Related to 'FengShi':**
*(search keywords like '风湿' or '风'&'湿' among herbs' 'Function')* 

*(Herbs' 'Function' is defined by herbal medicine theories, whereas 'Cure' are from patients' complains & symptoms )* 

```{r fs_hb_fun}

# ----------- Herbs Function FengShi ------------ 

fs_hb_fun <- readIn.func(fileName = "fs_hb_tres")

```

- **Among all <span style="color:red;fond=bold">`r length(unique(hb_nam$Corrected_ChName))`</span> herbs collected, there are <span style="color:red;fond=bold"> `r length(unique(fs_hb_fun$Corrected_ChName))` </span> herbs' Function contain the keyword '风湿' or '风'&'湿';**

- **Among these herbs which would theoretically function on FengShi, a word cloud of all the their 'Functions'(occurred >1 times) is shown below:**

<center>
```{r fs_hb_fun_wdcld}
fs_hb_fun_only <- select(fs_hb_fun,Treat)
funs <- data.frame(Treat=na.omit(unlist(fs_hb_fun_only)))
funs$Treat <- factor(funs$Treat,levels=as.character(names(sort(table(funs$Treat),decreasing=T))))
fun_freq <- as.data.frame(table(funs$Treat))
wordcloud(words=fun_freq$Var1,freq=fun_freq$Freq,min.freq=2,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8,'Dark2'))
```
</center>

- **From above word cloud, we can see '祛风除湿', which is a specific herb function targeting on FengShi, was selected;**
- **And beyond the functions target on FengShi('祛风除湿','祛风湿'), there are also functions like '清热解毒'(clear the body heat & toxic essences) & '活血止痛'(improve the blood flow & stop pain) found as highly correlated functions of the same group of herbs. And those functions would help improving the overall symptoms accompanied with FengShi.**

---

### **Explore the Herbal Prescriptions Could Cure FengShi:**

```{r fs_fj_cur}

# ----------- FangJi Cure FengShi ------------ 

fs_fj_cur <- readIn.func(fileName = "fs_fj_curs")

```

- **Among all <span style="color:red;fond=bold">`r length(unique(fj_nam$Corrected_ChName))`</span> herbal prescriptions collected, there are <span style="color:red;fond=bold">`r length(unique(fs_fj_cur$Corrected_ChName))`</span> of them contain the key work '风湿' or '风' & '湿';**

- **Among the prescriptions could cure FengShi, a word cloud of all their 'Cures'(or say symptoms, occurred >1 times) is shown below:**

<center>
```{r fs_fj_cur_wdcld}
fs_fj_cur_only <- select(fs_fj_cur,Symptom)
curs <- data.frame(Symptom=na.omit(unlist(fs_fj_cur_only)))
curs$Symptom <- factor(curs$Symptom,levels=as.character(names(sort(table(curs$Symptom),decreasing=T))))
cur_freq <- as.data.frame(table(curs$Symptom))
wordcloud(words=cur_freq$Var1,freq=cur_freq$Freq,min.freq=2,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8,'Dark2'))
```
</center>

- **And by exploring the prescriptions' components, a word cloud of the herbs' components(occurred >1 times) is shown below:**

```{r fs_fj_cmp}

# ----------- FangJi Cure FengShi Components ------------ 

fs_fj_cmp <- readIn.func(fileName = "fs_fj_cmps")

```

<center>
```{r fs_fj_cmp_wdcld}
fs_fj_cmp_only <- select(fs_fj_cmp,Component)
cmps <- data.frame(Component=na.omit(unlist(fs_fj_cmp_only)))
cmps$Component <- factor(cmps$Component,levels=as.character(names(sort(table(cmps$Component),decreasing=T))))
cmp_freq <- as.data.frame(table(cmps$Component))
wordcloud(words=cmp_freq$Var1,freq=cmp_freq$Freq,min.freq=2,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8,'Dark2'))
```
</center>

- **From above word cloud, and based on findings from other exploration, the herb <span style="color:green;fond=bold">'甘草'(Licorice)</span> was usually used as a mediator to harmony different herbs, so exclude '甘草', we see '防风', '当归', '羌活', '白术', '苍术', '川芎', '独活', '地黄' are highly involved in the prescriptions treating FengShi**
  - **A further exploration of the chemical constituents in these herbs are summarized below:**
      *(constituents in red are the same ingredients shown in different herbs)*

| **Herb** | **English Name** | **Main Chemical Constituents** | **Reference** |
| :--: | :---: | :----- | :--- |
| **防风** | Saposhnikovia divaricate |  5-O-甲基維斯阿米醇苷(5-O-methylvisammioside), 升麻素苷(prim-O-glucosylcimifugin), 升麻素 (cimifugin), 亥茅酚苷(sec-O-glucosylhamaudol), 亥茅酚(hamaudol), 香豆素(coumarin), 挥发油(volatile oil), etc | [防風化學成分與藥理研究進展](https://www.brion.org.tw/article-2-content.php?FatherNo=6&LevelNo=&Seq=8560&LevelName=%E4%B8%AD%E8%97%A5%E7%A7%91%E5%AD%B8%E6%96%B0%E7%9F%A5) |
| **当归** | Angelica sinensis | 黄樟醚(safrol), 异黄樟醚(isosafrol), <span style="color:red;fond=bold">佛手柑内酯(bergapten)</span>,  正丁基酜内酯(butylphthalide), <span style="color:red;fond=bold">藁本内酯(Ligustilide)</span>, 芹内酯(sedanonic acid lactone), <span style="color:red;fond=bold">花椒毒素(xanthotoxin)</span>, 异虎耳草素(isopimpinellin), 香荆芥酚(carvacrol), 苯戊酮邻羧酸(valerophenone-O-carboxylic acid), <span style="color:red;fond=bold">棕榈酸(palmitic acid)</span>, 崀菪葶(scopoletine), 繖形酮(umbelliferone), 香夹兰酸(vanillic acid), <span style="color:red;fond=bold">胆碱(choline)</span>, falcarinol | [当归化学成分的研究](https://tow.cnki.net/kcms/detail/detail.aspx?filename=YXXB197909003&dbcode=CRJT_CJFD&dbname=CRJT_CJFDTOTAL&v=) |
| **羌活** | Notopterygium incisum | 异欧前胡内酯(isoimperatorin 0.38%), 8-甲氧基异欧前胡内酯(cnidilin 0,5-羟基香柑素(notopterol) 1.2%), 香柑内酯(bergapten 0.009%), 5-羟基-8-(3,3-二甲基烯基)-补骨脂内酯(5-hydroxy-8(3,3-dimethylally)-psoralen,0.012%), 5-去甲基香柑醇(bergaptol 0.088%), 紫花前胡甙元(nodakenetin0.04%), 香柑醇-O-β-D-吡喃葡萄糖(bergaptol-O-β-D-glucopyranoside0.075%), 6-O-反-阿魏酰紫花前胡甙(6-O-trans-feruloylnodakenin0.022%), 二氢山芹醇(colrmbianetin), 二氢山芹醇甙(columbiananine), 欧前胡内酯(imperatorin), 印度榅桲素(marmesin), 对-羟基苯乙基茴香酸酯(p-ydroxyphenethylanisate 0.005%), <span style="color:red;fond=bold">阿魏酸(ferulicacid 0.89%)</span>, β-谷甾醇葡萄糖甙(β-sitosterolglucoside), β-谷甾醇(β-sitosterol), and a bunch more, pls see ref | [羌活百度百科](https://baike.baidu.com/item/%E7%BE%8C%E6%B4%BB/1789741)|
| **白术** | Atractylodes macrocephala | 蒼朮酮(Atractylon), 蒼朮醇(Atractylol), 白朮內酯I (Atractylenolide I), 白朮內酯II (Atractylenolide II), 白朮內酯III (Atractylenolide III), | [白朮化學成分與藥理研究進展](https://www.brion.org.tw/article-2-content.php?FatherNo=6&LevelNo=&Seq=8579&LevelName=)|
| **苍术** | Swordlike Atractylodes Rhizome | 苍术素(atractylodin), β-桉油醇(β-eudesmol), 茅术醇(hinesol), 羟基苍术酮(hydroxy-atractylon) | [苍术提取物百度百科](https://baike.baidu.com/item/%E8%8B%8D%E6%9C%AF%E6%8F%90%E5%8F%96%E7%89%A9/5592240) |
| **川芎** | Ligusticum chuanxiong Hort. | 川芎嗪(chuanxiongzine) / 四甲基吡嗪(te-tramethylpyrazine), 1-(5-羟甲基-2-呋喃基)-9h-吡啶并[3,4-b]吲哚(1-(5hydroxymethyl-2-furyl)-9H-pyrido[3，4-b]indole), <span style="color:red;fond=bold">藁本内酯(Ligustilide)</span>, 川芎萘呋内酯(wallichilide), 3-亚丁基苯酞(3-butylideniphthalide), 3-亚丁基-7-羟基苯酞(3-butylidene-7-hydroxyphthalide), (3S)-川芎酚((3S)-chunxiongol), 3-正丁基-3，6，7-三羟基-4，5，6，7-四氢苯酞(3-n-bntyl-3,6,7-trihydroxy-4,5,6,7-tetrahydrophthalide), 新川芎内酯(neocin-dilide), 洋川芎内酯(senkyunolide), 香草酸(vanillic acid), 咖啡酸(coffeic acid), 原儿茶酸(protocatechuic acid), <span style="color:red;fond=bold">阿魏酸(ferulic acid)</span>, 大黄酚(chrysophanic acid), 瑟丹酮酸(sedanonic acid), L-异亮氨酰-L-缬氨酸酐(L-isoleucyl-L-valine anhydride), L-缬氨酰-L-缬氨酸酐(L-valyl-L-valinc achydride), 黑麦草碱(perlolyrine), <span style="color:red;fond=bold">氯化胆碱(chloine chloride)</span>, <span style="color:red;fond=bold">棕榈酸(palmitic acid)</span>, 香草醛(vanillin) | [川芎百度百科](https://baike.baidu.com/item/%E5%B7%9D%E8%8A%8E/727831) |
| **独活** | | 甲氧基欧芹素(Osthole), 二氢欧山芹素(Columbianedin), 二氢欧山芹醇乙酸酯(Columbianetin acetate), 二氢欧山芹醇(Columbianetin), <span style="color:red;fond=bold">佛手柑内酯(Bergapten)</span>, 欧芹烯酚(Osthenol), 当归醇(Angelol), <span style="color:red;fond=bold">花椒毒素(Xanthotoxin)</span>,  异欧前胡素(Isoimperatorin), 异当归醇(Isoangelol), 毛当归醇(Anpubesol), 二氢欧山芹醇葡萄糖苷(Columbianetin-β-D-glucopyranoside), 伞形香豆素(Umbelliferone), 尤劳帕替醇(Ulopterol), 彼西丹醇(Peucedanol), 水合氧化前胡素(Oxypeucedanin hydrate), 紫花前胡苷(Nodakenin), 阿彼斯基姆素(Apiosylskimmin), 胡萝卜苷(Daucosterol), 腺苷(Adenosine) | [独活知乎](https://zhuanlan.zhihu.com/p/425357694) |
| **地黄** | Rehmanniaglutinosa | 梓醇(Catalpol), 桃叶珊瑚苷(Aucubin), 地黄苷A,B,C,D(Rehmannioside A,B,C,D), 胡萝卜苷(Daucosterol), 8-表番木鳖酸(8-Epiloganic acid), 水苏糖(Stachyose), 棉子糖(Raffinose), 苯甲酸(Benzoic acid), 辛酸(Caprylic acid), β-谷甾醇(β-Sitosterol), 豆甾醇(Stigma sterol),益母草苷(Leonuride) | [地黄知乎](https://zhuanlan.zhihu.com/p/259282898) |

---