---
title: "Herbs' Characters & Functions"
---

```{r include=FALSE}
knitr::opts_chunk$set(echo=FALSE, comment = NA, message=FALSE, warning=FALSE) #<--this will remove comments, messages, & warnings
```

```{r libSets, echo=FALSE, message=FALSE, comment=NA, warnings=F}

#Sys.setlocale(locale="Chinese")

library("googlesheets4")
library("tidyverse")
library("tidygraph")
library("table1")
library("readxl")
library("wordcloud")
library("knitr")
library("gridExtra")
#library("ggraph")
#library("ggplot2")
#library("grid")

gs4_deauth()

filePath <- "C:/Users/Sean/Documents/DigitCoral/DigitHerb/Cleaned/"
readIn.func <- function(fileName){
  read_excel(paste0(filePath,fileName,".xlsx"))
}
```

<br>

### **The Herbs Data Contains: Herbs' Name(药名), Property(药性), Taste(药味), Attribute(归经), Function(功能), Treatment(主治), & Toxicity(毒性)**

- Name: include cleaned Chinese Names, PinYin (the unique index variable), English Names, & Latin Names (English/Latin Names are under imputing)
- Property (药性): which clusters the herbs into 4 basic categories: Cold(寒), Cool(凉), Warm(温), Hot(热); (there are minor variations of the basic categories, such as Minor Cold(微寒), Minor Warm(微温), etc (the frequency of herbs properties in real world are listed in Property section below). <br>
  Whether we can cluster/combine the minor variations into equivalent categories will be further studied.
- Taste (药味):
- Attribute (归经):
- Function (功能):
- Treatment (主治):
- Toxicity (毒性):
  - Not all herb records had toxicity information, the missing might be considered as no toxic, although some herbs marked as No toxic in an obvious way.

```{r hb_nam}

# ----------- Herb Names (药名) ------------ 

#rw_hb_nam <- read_sheet("https://docs.google.com/spreadsheets/d/1rnQQsMh_PWMYAC9ukgtP-HTn5gkkceOQL6-XiHUVrKU/edit?usp=sharing",
#                        sheet = "Sheet1")
rw_hb_nam <- readIn.func(fileName = "Copy of HerbNames_v210807")
hb_nam <- rw_hb_nam[,c('Corrected_ChName','PinYin','EngName1','LatinName')]
```

<br>

#### **There are <span style="color:red;fond=bold"> **`r length(unique(hb_nam$Corrected_ChName))`** </span> herbs' info collected from different sources.** 

<br>

#### **Example of the Names of Herbs as Collected & Cleaned:**

```{r hb_nam_exampl,message=FALSE}
head(hb_nam) 
#d <- head(hb_nam)
#grid.table(d)
```

- The English / Latin Names are still need to do more imputation & verification.

<br>

--- 

```{r hb_pro}

# ---------- Herb Property (药性) Part ----------

#rw_hb_pro <- read_sheet("https://docs.google.com/spreadsheets/d/10fEh8pSETj3H5EI1Ud9Kqrc-jD4hqBr63Ytw2l7jtrw/edit?usp=sharing",
#                        sheet = "Sheet1")
rw_hb_pro <- readIn.func(fileName="Copy of HerbProperties_v210807")
hb_pro <- select(rw_hb_pro,Corrected_ChName,PinYin,Property1:Property3)
```

#### **Example of Herb Properties (药性) from above collections:**

```{r hb_pro_exampl}
head(hb_pro[,c('Corrected_ChName','PinYin','Property1')])
#grid.table(hb_pro[1:5,c('Corrected_ChName','PinYin','Property1')])
```

<br>

#### **Frequencties of Properties:** (since there might be 1 herb has >1 properties, so the overall # below is greater than <span style="color:red;fond=bold"> `r length(unique(hb_nam$Corrected_ChName))` </span>)

<br>

<center>
```{r hb_pro_st}
hb_pro_only <- select(hb_pro,Property1:Property3)
pros <- data.frame(Property=na.omit(unlist(hb_pro_only)))
pros$Property <- factor(pros$Property,levels=as.character(names(sort(table(pros$Property),decreasing=T))))
table1::table1(~Property, data=pros, topclass="Rtable1-zebra")
#above 2 lines sort output table by freq
``` 
</center>

---

```{r hb_tas}

# -------------- Herb Taste (药味) --------------

#rw_hb_tas <- read_sheet("https://docs.google.com/spreadsheets/d/12OwcITTME3Rfa3V91mckTqmL7ItsLq5vmrGw_wT9dE8/edit?usp=sharing",
#                        sheet = "Sheet1")
rw_hb_tas <- readIn.func(fileName = "Copy of HerbTastes_v210811")
#summary(rw_hb_tas)
hb_tas <- select(rw_hb_tas,Corrected_ChName,PinYin,Taste1:Taste6)
```

#### **Example of Herb Taste (药味) from above collections:**

```{r hb_tas_exampl}
hb_tas_ <- hb_tas[,c('Corrected_ChName','PinYin','Taste1')]
head(hb_tas_)
#grid.table(hb_tas[1:5,c('Corrected_ChName','PinYin','Taste1')])
```

<br>

#### **Frequencies of Tastes:** (since there might be 1 herb has >1 tastes, so the overall # below is greater than <span style="color:red;fond=bold"> `r length(unique(hb_nam$Corrected_ChName))` </span>)

<br>

<center>
```{r hb_tas_st}
hb_tas_only <- select(hb_tas,Taste1:Taste5)
tass <- data.frame(Taste=na.omit(unlist(hb_tas_only)))
tass$Taste <- factor(tass$Taste,levels=as.character(names(sort(table(tass$Taste),decreasing=T))))
table1::table1(~Taste, data=tass, topclass="Rtable1-zebra")
```
</center>

---

```{r hb_atr, echo=F, message=F,comment=F, warnings=F}

# -------------- Herb Attribute (归经) --------------

#rw_hb_atr <- read_sheet("https://docs.google.com/spreadsheets/d/1SfcnlGZ33d5zsTxbrYqiWS9QBiGPtoVp-ayM4ZMwgOU/edit?usp=sharing",
#                        sheet = "Sheet1")
rw_hb_atr <- readIn.func(fileName = "Copy of HerbAttributes_v210811c")
#summary(rw_hb_atr)
hb_atr <- select(rw_hb_atr,Corrected_ChName,PinYin,Attribute1:Attribute12)
```

#### **Example of Herb Attribute (归经) from above collections:**
```{r hb_atr_exampl}
head(hb_atr[,c('Corrected_ChName','PinYin','Attribute1')])
#grid.table(hb_atr[1:5,c('Corrected_ChName','PinYin','Attribute1')])
```

<br>

#### **Frequencies of Attributes:** (since there might be 1 herb has >1 Attributes, so the overall # below is greater than <span style="color:red;fond=bold"> `r length(unique(hb_nam$Corrected_ChName))` </span>)

<br>

<center>
```{r hb_atr_st}
hb_atr_only <- select(hb_atr,Attribute1:Attribute12)
atrs <- data.frame(Attribute=na.omit(unlist(hb_atr_only)))
atrs$Attribute <- factor(atrs$Attribute,levels=as.character(names(sort(table(atrs$Attribute),decreasing=T))))
table1::table1(~Attribute, data=atrs, topclass="Rtable1-zebra")
```
</center>

---

```{r hb_tox}
# ------------------------ Herb Toxicity(毒性) ---------------------------- #

#rw_hb_tox <- read_sheet("https://docs.google.com/spreadsheets/d/1B-yVSW6y5lZmQfihP5BxgkB4Y9KYZAcdec3PhhHzOPc/edit?usp=sharing",
#                        sheet = "Sheet1")
rw_hb_tox <- readIn.func(fileName = "Copy of HerbToxicities_v210813")
#summary(rw_hb_tox)
hb_tox <- select(rw_hb_tox,Corrected_ChName,PinYin,Toxicity)
```

#### **Example of Herb Toxicity (毒性) from above collections:**
```{r hb_tox_exampl}
head(hb_tox[,c('Corrected_ChName','PinYin','Toxicity')])
#grid.table(hb_tox[1:5,c('Corrected_ChName','PinYin','Toxicity')])
```

<br>

#### **Frequencies of Toxicities:** (since not all herbs had a clear toxicity record, so the overall # below is much less than <span style="color:red;fond=bold"> `r length(unique(hb_nam$Corrected_ChName))` </span>)

<br>

<center>
```{r hb_tox_st}
hb_tox_only <- select(hb_tox,Toxicity)
toxs <- data.frame(Toxicity=na.omit(unlist(hb_tox_only)))
toxs$Toxicity <- factor(toxs$Toxicity,levels=as.character(names(sort(table(toxs$Toxicity),decreasing=T))))
table1::table1(~Toxicity, data=toxs, topclass="Rtable1-zebra")
```
</center>

---

```{r hb_fun}

# -------------- Herb Function (功能) --------------

#rw_hb_fun <- read_sheet("https://docs.google.com/spreadsheets/d/1OfXvaCWTp4qMcHHoMaUrD_3xaeWZc0uasuAQzf1ylYc/edit?usp=sharing",
#                        sheet = "Sheet1")
rw_hb_fun <- readIn.func(fileName = "Copy of HerbFunctions_v210809")
#summary(rw_hb_fun)
hb_fun <- select(rw_hb_fun,Corrected_ChName,PinYin,Function1:Function13)
```

#### **Example of Herb Function (功能) from above collections:**
```{r hb_fun_exampl}
head(hb_fun[,c('Corrected_ChName','PinYin','Function1')])
#grid.table(hb_fun[1:5,c('Corrected_ChName','PinYin','Function1')])
```

<br>

```{r qOut1}
#### **Frequencies of Functions:** (since there might be 1 herb has >1 Functions, so the overall # below is greater than <span style="color:red;fond=bold"> `r length(unique(hb_nam$Corrected_ChName))` </span>)
```
#### **A Wordcloud chart of the first 200 herb functions is shown below:**

<center>
```{r hb_fun_st}
hb_fun_only <- select(hb_fun,Function1:Function13)
funs <- data.frame(Function=na.omit(unlist(hb_fun_only)))
funs$Function <- factor(funs$Function,levels=as.character(names(sort(table(funs$Function),decreasing=T))))
#table1::table1(~Function, output.lines=10, data=funs, topclass="Rtable1-zebra")
fun_freq <- as.data.frame(table(funs$Function))
wordcloud(words=fun_freq$Var1,freq=fun_freq$Freq,min.freq=1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8,'Dark2'))
```
</center>

---

```{r hb_tre}

# -------------- Herb Treatment (主治) --------------

#rw_hb_cur <- read_sheet("https://docs.google.com/spreadsheets/d/1Il7wflxanzNrX1_PUrVeHot5qrF_pK2BEPTTuCm2s5g/edit?usp=sharing",
#                        sheet = "Sheet1")
rw_hb_cur <- readIn.func(fileName = "Copy of HerbCures_v210809")
#summary(rw_hb_fun)
hb_cur <- select(rw_hb_cur,Corrected_ChName,PinYin,Cure1:Cure40)
```

#### **Example of Herb Treatment (主治) from above collections:**
```{r hb_cur_exampl}
head(hb_cur[,c('Corrected_ChName','PinYin','Cure1')])
#grid.table(hb_cur[1:5,c('Corrected_ChName','PinYin','Cure1')])
```

<br>

#### **A Wordcloud chart of the first 200 herb treatments is shown below:**

<center>
```{r hb_cur_st}
hb_cur_only <- select(hb_cur,Cure1:Cure40)
curs <- data.frame(Treatment=na.omit(unlist(hb_cur_only)))
curs$Treatment <- factor(curs$Treatment,levels=as.character(names(sort(table(curs$Treatment),decreasing=T))))
#table1::table1(~Treatment, output.lines=10, data=curs, topclass="Rtable1-zebra")
cur_freq <- as.data.frame(table(curs$Treatment))
wordcloud(words=cur_freq$Var1,freq=cur_freq$Freq,min.freq=1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8,'Dark2'))
```
</center>