---
title: "Prescriptions' Functions & Cures"
---

```{r include=FALSE}
knitr::opts_chunk$set(echo=FALSE, comment = NA, message=FALSE, warning=FALSE) #<--this will remove comments, messages, & warnings
```

```{r libSets, echo=FALSE, message=FALSE}
library("googlesheets4")
library("tidyverse")
library("tidygraph")
library("ggraph")
library("googlesheets4")
library("table1")
library("readxl")
library("wordcloud")
library("gridExtra")
library("knitr")
#### this paragraph is the knit_hook created by yihui to reduce results lines
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  lines <- options$output.lines
  if (is.null(lines)) {
    return(hook_output(x, options))  # pass to default hook
  }
  x <- unlist(strsplit(x, "\n"))
  more <- "..."
  if (length(lines)==1) {        # first n lines
    if (length(x) > lines) {
      # truncate the output, but add ....
      x <- c(head(x, lines), more)
    }
  } else {
    x <- c(more, x[lines], more)
  }
  # paste these lines together
  x <- paste(c(x, ""), collapse = "\n")
  hook_output(x, options)
})
#### ^-- end of knit_hook

gs4_deauth()
filePath <- "C:/Users/Sean/Documents/DigitCoral/DigitHerb/Cleaned/"
readIn.func <- function(fileName){
  read_excel(paste0(filePath,fileName,".xlsx"))
}
```

```{r hb_nam, echo=F, message=F,comment=F, warnings=F}

# ----------- Prescription Names (方剂名) ------------ 

#rw_fj_nam <- read_sheet("https://docs.google.com/spreadsheets/d/10cbNUzwSzDi16HPnpVaFIKqzaaAl8ZcyiUyoQuvM10w/edit?usp=sharing",
#                        sheet = "Sheet1")
rw_fj_nam <-readIn.func(fileName = "FangJiNames_v210822")
fj_nam <- rw_fj_nam[,c('Original_ChName','Corrected_ChName','PinYin','Reference')]
```

<br>

#### **There are <span style="color:red;fond=bold"> **`r length(unique(fj_nam$Original_ChName))`** </span> Prescripts' info collected from different sources.** 
#### **Since one prescription could have more than 1 variations of components or doses, the real prescription lines are <span style="color:red;fond=bold"> **`r length(unique(fj_nam$Corrected_ChName))`** </span>.**

- The Prescription Data Contains: Prescription Names(方剂名), Components(方剂组成), Functions(方剂功能) & Cures(方剂主治)

#### **Example of the Names of Prescriptions as Collected & Cleaned:**
```{r fj_nam_exampl, echo=F, message=F,comment=NA, warnings=F}
fj_nam_ <- fj_nam[,c('Corrected_ChName','PinYin','Reference')]
head(fj_nam_)
```
- **The Chinese Prescription Names are pending to translated into English.**

--- 

```{r fj_cmp, echo=F, message=F,comment=F, warnings=F}

# ---------- Prescription Components (方剂组成) Part ----------

#rw_fj_cmp <- read_sheet("https://docs.google.com/spreadsheets/d/1f2dWSApp9JjCfK82lbZ1Kf-7ZAlV8f-ntP_6Dio_DPw/edit?usp=sharing",
#                        sheet = "Sheet1")
rw_fj_cmp <- readIn.func(fileName = "FangJiComponents_v210822")
fj_cmp <- select(rw_fj_cmp,Corrected_ChName,PinYin,Compo1:Compo86)
```

#### **Example of Prescription Components (方剂组成) from above collections:(there are 86 component columns, below only show the first 5 of them)**
```{r fj_cmp_exampl, echo=F, message=F,comment=NA, warnings=F}
head(fj_cmp[,c('Corrected_ChName','PinYin','Compo1','Compo2','Compo3','Compo4','Compo5')])
```
- **Components context & doses will be further cleaned.**

#### **A Wordcloud chart of the first 200 prescriptions' herb components is shown below:**

<center>
```{r fj_cmp_st, output.lines=10, echo=F, message=F,comment=F, warnings=F}
fj_cmp_only <- select(fj_cmp,Compo1:Compo86)
cmps <- data.frame(Component=na.omit(unlist(fj_cmp_only)))
cmps$Component2 <- sub("[0-9+()].*","",cmps$Component) #<--substr anything before a delimiter (if need after, use .* before the [])
cmps2 <- cmps[!(cmps$Component2=="#VALUE!"),]
cmps2$Component2 <- factor(cmps2$Component2,levels=as.character(names(sort(table(cmps2$Component2),decreasing=T))))
#table1::table1(~Function, output.lines=10, data=funs, topclass="Rtable1-zebra")
cmp_freq <- as.data.frame(table(cmps2$Component2))
wordcloud(words=cmp_freq$Var1,freq=cmp_freq$Freq,min.freq=1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8,'Dark2'))
```
</center>

---

```{r fj_cur, echo=F, message=F,comment=F, warnings=F}

# ---------- Prescription Treatments (方剂主治) Part ----------

#rw_fj_cur <- read_sheet("https://docs.google.com/spreadsheets/d/1K-m_s0Zb_NetpaSNESLDVm_qpWkN9QevBA_BxsGiEGI/edit?usp=sharing",
#                        sheet = "Sheet1")
rw_fj_cur <- readIn.func(fileName = "FangJiCures_v210822")
fj_cur <- select(rw_fj_cur,Corrected_ChName,PinYin,Cure1:Cure60)
```

#### **Example of Prescription Treatments (方剂主治) from above collections:(there are 60 Cure columns, below only show the first 5 of them)**
```{r fj_cur_exampl, echo=F, message=F,comment=NA, warnings=F}
head(fj_cur[,c('Corrected_ChName','PinYin','Cure1','Cure2','Cure3','Cure4','Cure5')])
```
- **Prescription Function & treatments will be further cleaned.**

#### **A Wordcloud chart of the first 200 prescriptions' treatments is shown below:**

<center>
```{r fj_cur_st, output.lines=10, echo=F, message=F,comment=F, warnings=F}
fj_cur_only <- select(fj_cur,Cure1:Cure60)
fj_curs <- data.frame(Treatment=na.omit(unlist(fj_cur_only)))
fj_curs$Treatment2 <- sub("[0-9+()].*","",fj_curs$Treatment) #<--substr anything before a delimiter (if need after, use .* before the [])
fj_curs2 <- fj_curs[!(fj_curs$Treatment2=="#VALUE!"),]
fj_curs2$Treatment2 <- factor(fj_curs2$Treatment2,levels=as.character(names(sort(table(fj_curs2$Treatment2),decreasing=T))))
#table1::table1(~Function, output.lines=10, data=funs, topclass="Rtable1-zebra")
cur_freq <- as.data.frame(table(fj_curs2$Treatment2))
wordcloud(words=cur_freq$Var1,freq=cmp_freq$Freq,min.freq=1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8,'Dark2'))
```
</center>